\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-24 paper.tex
change H to E

In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
We have a system energy $ H $ 
\os{change to E}
of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
The Hamiltonian dynamics is determined by the gradients of the system energy, which is
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
%
The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
If two different states have the same energy, the probabilities of them are equivalent.
It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
%
Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
The momentum $ q $ is used as an auxiliary variable.
Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Old text that may be re-used
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density. Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods. Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.

>>>>

In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
We have a system energy $ E $ 
%\os{change to E}
of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ E(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
The Hamiltonian dynamics is determined by the gradients of the system energy, which is
$ \frac{dx}{dt} = \frac{\partial E}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial E}{\partial x} $.
%
The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -E(x,q) / T ) $.
If two different states have the same energy, the probabilities of them are equivalent.
It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
%
Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
The momentum $ q $ is used as an auxiliary variable.
Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Old text that may be re-used
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density. Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods. Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.
